Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-24 papers/actus2021/article.tex
typo fixed

In this paper we explore ways in which contracts described in ACTUS (Algorithmic Contract Types Unified Standards) can be defined in the contract langauges Marlowe, Plutus and Haskell. Of course, Plutus or Haskell are able to express these contracts, but rendering them in Marlowe brings extra advantages. Marlowe is defined to provide a range of guarantees by design: a Marlowe contract will only make a finite number of interactions with its environment, and its lifetime can be read off from the code for a contract; moreover, when the contract terminates, any assets held by the contract will automatically be returned to the participants. None of these guarantees can be provided by a general purpose language.

>>>>

In this paper we explore ways in which contracts described in ACTUS (Algorithmic Contract Types Unified Standards) can be defined in the contract languages Marlowe, Plutus and Haskell. Of course, Plutus or Haskell are able to express these contracts, but rendering them in Marlowe brings extra advantages. Marlowe is defined to provide a range of guarantees by design: a Marlowe contract will only make a finite number of interactions with its environment, and its lifetime can be read off from the code for a contract; moreover, when the contract terminates, any assets held by the contract will automatically be returned to the participants. None of these guarantees can be provided by a general purpose language.
